My English activity log

### 2019-11-10 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
chgmt my english activity log
ajout image
jusqu'au 10/11/2019

---
title: "My english activity log"
---

@@

>>>>

---
title: "My English activity log"

author:
  - name: Aurélie Pinchart
date: 11-04-2019
preview: english.jpg
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

05/11/2019 : I watched a video about ethology (the second part) https://www.youtube.com/watch?v=jEZIUVU0BCU.

07/11/2019 : I watched  the last part of the video about ethology https://www.youtube.com/watch?v=bspxe_-ilC4.

09/11/2019 : I watched a video about enzymes https://www.youtube.com/watch?v=6Acx6b3Hzsk 
10/11/2019 : I watched a video about germination https://www.youtube.com/watch?v=cmzhvl5kOc0 and I read the seventh chapter of "The Hobbit".
